Comparison of Spatial Partitioning Strategies

### 2025-01-23 paper/paper.tex
Abstract has been writen and inserted image for quadtree.

\usepackage[utf8]{inputenc} % For UTF-8 encoding
\usepackage[english]{babel} % For English language settings
% \usepackage{amsmath}        % For mathematical symbols
% \usepackage{graphicx}       % For including images
% \usepackage{hyperref}       % For hyperlinks
\usepackage[margin=1in]{geometry}       % To set margins
% \usepackage{float}          % For controlling figure placement
% \usepackage{booktabs}       % For better table formatting

\renewcommand{\baselinestretch}{1.15}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\title{Comparison of Spatial Partitioning Strategies}
\author{Linus Kåreblom}
\date{\today}

@@

\begin{abstract}
    This is the abstract of my paper.
\end{abstract}

@@

\subsection{Quadtree}
A quadtree is a recursive data structure, meaning it contains pointers to each
objects of the same type as itself. It's in the family of tree data structures.
The data structure is comprised of nodes. Each node has four pointers to other
nodes, could also be referred to as branches.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{svg}

\renewcommand{\baselinestretch}{1.15}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\graphicspath{ {../graphs/} }

@@

\begin{abstract}
    Spatial partitioning is a widely used optimization strategy to efficiently
    optimize objects in space. It can be found in many applications, from
    simulating galaxies to video games.
    Checking collision between objects is an expensive operation that quickly
    becomes a bottleneck as the number of objects grow.
    This paper compares three different strategies, alongside a naive solution.
    The aim is to evaluate the use cases for the different strategies.
    Each strategy was implemented to fit the same interface to make it as fair
    of a comparison as possible.
    The results show how spatial hashing out performs every other method when
    the objects are distributed evenly while quadtrees excel with uneven object
    distribution.
\end{abstract}

@@

\subsection{Quadtree}
A quadtree is a recursive data structure, meaning it contains pointers to each
objects of the same type as itself. It's in the family of tree data structures.
The data structure is comprised of nodes. Each node has four pointers to other
nodes, could also be referred to as branches or leaves. This strategy works by
inserting points into a leaf until the leaf reaches its capacity, then it splits
into four equally large sub leaves. This subdivision pattern is shown in figure
\ref{fig:quadtree}.

\begin{figure}[ht]
    \includesvg[width=\textwidth]{images/invert-quadtree.svg}
    \caption{Visual representation of a quadtree.}
    \label{fig:quadtree}
\end{figure}
